The occurrence rate of long-period exoplanets

### 2016-02-17 document/ms.tex
figure fixes
a new figure

\documentclass[preprint]{aastex}

@@

\section{The search for long-period exoplanets}

Data from the \kepler\ Mission has been used to discover a diverse zoo of
thousands of exoplanets of all sizes orbiting stars of all types.
It has be demonstrated that these discoveries can be used to place constraints
on the occurrence rate of exoplanets \dfmtodo{CITE}.
These results are sensitive to the detection efficiency and reliability of the
transit discovery methods \dfmtodo{CITE Burke}.

The search for long-period planets presents several unique challenges.
Of these, the most important is the inevitable sensitively to signals falsely
identified as being caused by a transit exoplanet when it is actually a
systematic false alarm (noise) or an astrophysical false positive.
In the following paragraphs, we detail our method for addressing these
challenges and quantifying their effects.
In summary, we identify false alarms by developing a conservative automated
candidate vetting algorithm using the full light curve of each target star and
measure the incompleteness introduced by this procedure.
To account for astrophysical false positives, we discard candidates that fail
the standard transit centroid tests and then statistically incorporate
uncertainties introduced by false positives missed by this procedure at a
population level.

\section{Candidate vetting}

\paragraph{Light curve}

\begin{figure}[p]
\begin{center}
\includegraphics[width=\textwidth]{figures/model_comp.pdf}
\end{center}
\caption{%
Representative examples of candidate events flagged by the initial search.
Each example falls into a different model category and the figure shows the
data as black points and the best fit mean model prediction.
The examples represent the following model categories:
\emph{(a)} variability, \emph{(b)} step, \emph{(c)} box, and \emph{(d)}
transit.
\figlabel{model-comp}}
\end{figure}

@@

@@

\begin{figure}[p]
\begin{center}
\includegraphics{figures/full_sample.pdf}
\end{center}
\caption{%
Blah.
\figlabel{full-sample}}
\end{figure}

>>>>

\documentclass[twocolumn]{aastex6}
% \documentclass[onecolumn]{aastex6}
% \documentclass[preprint]{aastex}

@@

Data from the \kepler\ Mission has been used to discover a diverse zoo of
thousands of exoplanets of all sizes orbiting stars of all types.
It has be demonstrated that these catalogs of exoplanet discoveries can be
used to place constraints on the occurrence rate of exoplanets \dfmtodo{CITE}.
These results are sensitive to the detection efficiency and reliability of the
discovery methodology \dfmtodo{CITE Burke}.

\section{The fully-automated search for long-period exoplanets}

To find long-period exoplanets in the \kepler\ light curves, we search for
individual, high signal-to-noise transit signals using a fully-automated
procedure that can be broken into three main steps:
\begin{enumerate}
{\item an initial candidate search using a box-shaped matched filter,}
{\item light curve-level vetting (using automated model comparison) to remove
signals that don't match a transit shape, and}
{\item pixel-level vetting to remove some astrophysical false positives.}
\end{enumerate}
The following sections describe each of these steps in more detail.

% The search for long-period planets presents several unique challenges.
% Of these, the most important is the inevitable sensitively to signals falsely
% identified as being caused by a transit exoplanet when it is actually a
% systematic false alarm (noise) or an astrophysical false positive.
% In the following paragraphs, we detail our method for addressing these
% challenges and quantifying their effects.
% In summary, we identify false alarms by developing a conservative automated
% candidate vetting algorithm using the full light curve of each target star and
% measure the incompleteness introduced by this procedure.
% To account for astrophysical false positives, we discard candidates that fail
% the standard transit centroid tests and then statistically incorporate
% uncertainties introduced by false positives missed by this procedure at a
% population level.

\subsection{Finding box-shaped candidate events}

It is not feasible to compute a full model comparison at every time in the
light curve so we must first find potentially interesting events.
To generate this list, we apply a standard ``box least squares'' (BLS;
\dfmtodo{CITE}) method with a single (non-periodic) box.
First, we filter the PDC (\dfmtodo{CITE}) light curves using a running
windowed median with a half-width of \dfmtodo{how many} to remove stellar
variability.
We then compute the signal-to-noise of the depth of a 0.6~day long transit on
a grid of times spanning the full \kepler\ baseline.
To avoid edge effects, we apodize this detection scalar near any large gaps in
the time series using a logistic function with width equal to one transit
duration.
Finally, we estimate the noise in the time series using a robust running
windowed variance estimate of the detection scalar and accepting peaks more
than 25-times this noise as candidates.

\subsection{Light curve-level vetting}

\subsection{Pixel-level vetting}

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{figures/model_comp.pdf}
\end{center}
\caption{%
Representative examples of candidate events flagged by the initial search.
Each example falls into a different model category and the figure shows the
data as black points and the best fit mean model prediction.
The examples represent the following model categories:
\emph{(a)} variability, \emph{(b)} step, \emph{(c)} box, and \emph{(d)}
transit.
\figlabel{model-comp}}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics{figures/targets.pdf}
\end{center}
\caption{%
Blah.
\figlabel{targets}}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics{figures/full_sample.pdf}
\end{center}
\caption{%
Blah.
\figlabel{full-sample}}
\end{figure*}
